Blockchain Consensus Protocol with\\Horizontal Scalability

### 2017-08-26 presentation/presentation.tex
Add large throughput graph

\begin{frame}{The dangers of centralisation:~Examples}
  \begin{itemize}
    \item Baidu's promoted search result on experimental medical care caused death of a student~\cite{weizexi}
    \item Facebook can predict your opinions and desires better than your spouse~\cite{youyou2015computer}
    \item With intimate knowledge of the individuals,
      Facebook creates ``psychographic'' profiles in political campaigns~\cite{psychographic}
  \end{itemize}
  \note{
    \begin{itemize}
      \item The student had cancer---(synovial sarcoma)
      \item The treatment was phased out at clinical stage in the US because the success rate is too low
      \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
      completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
      answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
      Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
      with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
      of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
      outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
      words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
      predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
      \item Summary: we live in an age where companies and governments are able to control our thoughts,
      where is the freedom and liberty in that?
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{Blockchain:~not there yet}
  \begin{itemize}
    \item Early blockchain systems do not scale
    \item Bitcoin is limited to 7 transactions per second
    \item 100,000 transaction backlog in May 2017
    \item We require horizontal scalability for ubiquitous use
    \item More nodes = better performance and throughput
  \end{itemize}
\end{frame}

@@

\subsection{Research question}
\begin{frame}{\subsecname}
  \begin{block}{}
    \Large{
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and able to reach \emph{global consensus?}
    }
  \end{block}
    \note{
      \begin{itemize}
      \item Blockchain consensus protocol---independent of the application, like PoW (not PoS)
      \item Byzantine fault tolerance---if some number of nodes are malicious then the system should continue to function
      \item Horizontal scalability---if every node make transactions at the same rate, then the global throughput should increase
      \item Global consensus---all node should agree on a global state, useful for some applications, e.g. digital cash
      \end{itemize}
    }
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\label{def:consensus}
The consensus protocol has the following properties in every round $r$.
\begin{enumerate}
    \item \emph{Agreement}:
        Every correct outputs the same set of facilitators.
    \item \emph{Validity}:
      The consensus results is valid such that a new set of facilitators can be computed from it.
    \item \emph{Fairness}:
        Every node with a CP block in the consensus result should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        Every correct node eventually outputs a set of facilitators.
\end{enumerate}
\end{frame}

@@

\section{Conclusion}
\begin{frame}{\secname}
  \begin{block}{Research question}
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{scalable} and able to reach \emph{global consensus?}
  \end{block}
Our system achieve the following
\begin{itemize}
  \item Fault tolerant up to $t$ nodes
  \item Horizontal scalability
  \item Global consensus on CP blocks
\end{itemize}
\end{frame}

\begin{frame}{Future work}
\begin{itemize}
\item Improve fault tolerance
\item Improve fork detection
\item Analyse the system in the permissionless environment
\item Concrete application
\end{itemize}
\end{frame}

>>>>

\begin{frame}{The dangers of centralisation:~Examples}
  \begin{itemize}
    \item Facebook can predict your opinions and desires better than your spouse~\cite{youyou2015computer}
    \item With intimate knowledge of the individuals,
      Facebook creates ``psychographic'' profiles in political campaigns~\cite{psychographic}
    \item Baidu's promoted search result on experimental medical care caused death of a student~\cite{weizexi}
  \end{itemize}
  \note{
    \begin{itemize}
      \item The student had cancer---(synovial sarcoma)
      \item The treatment was phased out at clinical stage in the US because the success rate is too low
      \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
      completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
      answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
      Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
      with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
      of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
      outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
      words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
      predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
      \item Summary: we live in an age where companies and governments are able to control our thoughts,
      where is the freedom and liberty in that?
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{Blockchain:~not there yet}
  \begin{itemize}
    \item Consensus algorithm of early blockchain systems do not scale
    \item Bitcoin (PoW) is limited to 7 transactions per second
    \item 100,000 transaction backlog in May 2017
    \item We require horizontal scalability for ubiquitous use
    \item More nodes = better performance and throughput
  \end{itemize}
\end{frame}

@@

\subsection{Research question}
\begin{frame}{\subsecname}
  \begin{block}{}
    \Large{
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault-tolerant},
    \emph{horizontally scalable}, and able to reach \emph{global consensus?}
    }
  \end{block}
    \note{
      \begin{itemize}
      \item Blockchain consensus protocol---independent of the application, like PoW (not PoS)
      \item Byzantine fault tolerance---if some number of nodes are malicious then the system should continue to function
      \item Horizontal scalability---if every node make transactions at the same rate, then the global throughput should increase
      \item Global consensus---all node should agree on a global state, useful for some applications, e.g. digital cash
      \end{itemize}
    }
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\label{def:consensus}
The consensus protocol has the following properties in every round $r$.
\begin{itemize}
    \item \emph{Agreement}:
        Every correct outputs the same set of facilitators.
    \item \emph{Validity}:
      The consensus results is valid such that a new set of facilitators can be computed from it.
    \item \emph{Fairness}:
        Every node with a CP block in the consensus result should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        Every correct node eventually outputs a set of facilitators.
\end{itemize}
\end{frame}

@@

\begin{frame}{Throughput vs population size (fixed neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{throughput-vs-population-large}
  \centering
  \end{figure}
\end{frame}

\section{Conclusion}
\begin{frame}{\secname}
  Out work answers the research question.
  \begin{block}{}
    How can we design a \emph{blockchain consensus protocol} that is \emph{fault tolerant},
    \emph{horizontally-scalable}, and able to reach \emph{global consensus?}
  \end{block}
\end{frame}

\begin{frame}{Future work}
\begin{itemize}
\item Implement and experiment with a concrete application
\item Analyse the system in the permissionless environment
\item Improve fault tolerance
\end{itemize}
\end{frame}
